\chapter{Acknowledgements}
\label{thanks}
% \setcounter{page}{1}
First and foremost, we would like to extend our heartfelt appreciation to our advisors, Dr. Le Trung Nghia and Assoc. Prof. Tran Minh Triet, for their invaluable guidance and unwavering support throughout the completion of this thesis. Their expertise, constant encouragement, constructive feedback and inspirational motivation have played a pivotal role in moulding the progress of this thesis. We are deeply grateful for their helpful advice, which not only helps us in this thesis but also in terms of professional work ethic and attitude.

Secondly, we want to express our gratitude to the Faculty of Information Technology members at the University of Science, VNU-HCM. Their knowledge and guidance have profoundly influenced our academic journey and fostered a strong foundation for us to carry out this research. 
% The valuable lessons, suggestions, and discussions provided by these esteemed individuals have significantly enhanced our understanding of the topic and enriched the quality of our work.

We are also indebted to our teachers and friends at SELAB and Honors Program Class 19, Faculty of Information Technology at the University of Science, VNU-HCM, for their support, advice, and assistance throughout our process.

Last but not least, we express our deep gratitude to our family, whose belief in us and persistent presence. Their unconditional love, unwavering encouragement, and immeasurable have been a constant source of motivation to help us in the accomplishment of this thesis but also throughout our entire learning journey.

This thesis would not have come to fruition without the collective contributions and support of all those mentioned above, and for that, we are truly grateful.

% Le Khanh Duy, Do Trong Le 
% In particular, we express our profound appreciation to Mr. Nguyen Nhat Minh Khoi for his valuable assistance with the device during the application demo. 
% Additionally, we would like to acknowledge and thank Ms. Trinh Thi Thuy for her gracious involvement as an actor in the demo video, which greatly enhanced the presentation of our work.

% We are particularly grateful to Mr. Le Tan Dang Khoa, Lê Minh Tú, Hoang-Khang Nguyen, Shruti Singh, Vinay, Duc Thanh, Zen, Bạch Sỹ Khang, Quan, and numerous anonymous users who generously participated in our survey. Their willingness to provide support and offer invaluable insights have been instrumental in the success of this thesis.