\chapter*{List of Publications}
\label{publication}

\begin{enumerate}
    \item \textbf{Khoi-Nguyen Nguyen-Ngoc}*, \textbf{Thanh-Tung Phan-Nguyen}*, Khanh-Duy Le, Tam V. Nguyen Minh-Triet Tran, Trung-Nghia Le. Dm-vton: Distilled mobile real-time virtual try-on. Accepted for \uline{IEEE International Symposium on Mixed and Augmented Reality (ISMAR)}, 2023.
    \item Tuan-Luc Huynh, \textbf{Khoi-Nguyen Nguyen-Ngoc}, Chi-Bien Chu, Minh-Triet Tran, Trung-Nghia Le. Multilingual Communication System with Deaf Individuals Utilizing Natural and Visual Languages. In \uline{RIVF International Conference on Computing and Communication Technologies (RIVF)}, 2022.
    \item Jie Qin and Shuaihang Yuan and Jiaxin Chen and Boulbaba {Ben Amor} and Yi Fang and Nhat Hoang-Xuan and Chi-Bien Chu and \textbf{Khoi-Nguyen Nguyen-Ngoc} and Thien-Tri Cao and Nhat-Khang Ngo and Tuan-Luc Huynh and Hai-Dang Nguyen and Minh-Triet Tran and Haoyang Luo and Jianning Wang and Zheng Zhang and Zihao Xin and Yang Wang and Feng Wang and Ying Tang and Haiqin Chen and Yan Wang and Qunying Zhou and Ji Zhang and Hongyuan Wang. SHREC’22 track: Sketch-based 3D shape retrieval in the wild. In \uline{Computers \& Graphics}, 2022.
    \item Chiara Romanengo and Andrea Raffo and Silvia Biasotti and Bianca Falcidieno and Vlassis Fotis and Ioannis Romanelis and Eleftheria Psatha and Konstantinos Moustakas and Ivan Sipiran and Quang-Thuc Nguyen and Chi-Bien Chu and \textbf{Khoi-Nguyen Nguyen-Ngoc} and Dinh-Khoi Vo and Tuan-An To and Nham-Tan Nguyen and Nhat-Quynh Le-Pham and Hai-Dang Nguyen and Minh-Triet Tran and Yifan Qie and Nabil Anwer. SHREC 2022: Fitting and recognition of simple geometric primitives on point clouds. In \uline{Computers \& Graphics}, 2022.
\end{enumerate}